---
title: "Topic 3: Proteome-wide Screen for RNA-dependent Proteins; Subtopic 3: HeLa synchronized in Interphase"
author: "Hannah, Johann, Kira, Viktor"
date: "2023-04-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Topic 3: Proteome-wide Screen for RNA-dependent Proteins

#### Subtopic 3: HeLa Cells Synchronized in Interphase

First, we will load the dataset containing the mass spectrometry data from HeLa cells synchronized in interphase:

```{r}
RDeeP_HeLa_Interphase = read.csv("https://www.dropbox.com/s/nm9bgsyg7cv6wu1/RDeeP_HeLa_Interphase.csv?dl=1", header=TRUE, row.names=1, sep = ";")
head(RDeeP_HeLa_Interphase)
```

Are there any missing values in the dataset?

```{r}
sum(is.na(RDeeP_HeLa_Interphase))
```

Are there any rows that only contain zeros?

```{r}
which(rowSums(RDeeP_HeLa_Interphase)==0)
```

We can also split the dataset into two seperate datasets that contain the Control and RNase values:
#### 1.1 Split Dataset into Control and RNase

```{r}
RDeeP_HeLa_Interphase_Ctrl = cbind(RDeeP_HeLa_Interphase[,1:3],RDeeP_HeLa_Interphase[,7:9],RDeeP_HeLa_Interphase[,13:15],RDeeP_HeLa_Interphase[,19:21],RDeeP_HeLa_Interphase[,25:27],RDeeP_HeLa_Interphase[,31:33],RDeeP_HeLa_Interphase[,37:39],RDeeP_HeLa_Interphase[,43:45],RDeeP_HeLa_Interphase[,49:51],RDeeP_HeLa_Interphase[,55:57],RDeeP_HeLa_Interphase[,61:63],RDeeP_HeLa_Interphase[,67:69],RDeeP_HeLa_Interphase[,73:75],RDeeP_HeLa_Interphase[,79:81],RDeeP_HeLa_Interphase[,85:87],RDeeP_HeLa_Interphase[,91:93],RDeeP_HeLa_Interphase[,97:99],RDeeP_HeLa_Interphase[,103:105],RDeeP_HeLa_Interphase[,109:111],RDeeP_HeLa_Interphase[,115:117],RDeeP_HeLa_Interphase[,121:123],RDeeP_HeLa_Interphase[,127:129],RDeeP_HeLa_Interphase[,133:135],RDeeP_HeLa_Interphase[,139:141],RDeeP_HeLa_Interphase[,145:147])
RDeeP_HeLa_Interphase_RNase=RDeeP_HeLa_Interphase[,-which(names(RDeeP_HeLa_Interphase) %in% colnames(RDeeP_HeLa_Interphase_Ctrl))]
```

#### 1.2 NA Values and Zero Rows
```{r}
## Überprüfen welche Reihen in den Datasets nur Nullen enthalten

which(rowSums(RDeeP_HeLa_Interphase_Ctrl)==0)
which(rowSums(RDeeP_HeLa_Interphase_RNase)==0)

## Löschen der Nullreihen im Controldataset

RDeeP_HeLa_Interphase_Ctrl <- RDeeP_HeLa_Interphase_Ctrl[!(rownames(RDeeP_HeLa_Interphase_Ctrl)%in% c("FHOD3_HUMAN","P210L_HUMAN","PKD1_HUMAN","TGM7_HUMAN","KIF1A_HUMAN")),]

##Löschen der Nullreihen im RNase-Dataset

RDeeP_HeLa_Interphase_RNase <- RDeeP_HeLa_Interphase_RNase[!(rownames(RDeeP_HeLa_Interphase_RNase) %in% c("FHOD3_HUMAN","P210L_HUMAN","PKD1_HUMAN","TGM7_HUMAN", "KIF1A_HUMAN")),]
```

#### 1.4 Mean of Replicates

```{r}

# calculate mean of triplicates for each fraction split into seperate datasets

M_RNase_01 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,1:3], 1, function(x) {mean(x)}))
M_RNase_02 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,4:6], 1, function(x) {mean(x)}))
M_RNase_03 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,7:9], 1, function(x) {mean(x)}))
M_RNase_04 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,10:12], 1, function(x) {mean(x)}))
M_RNase_05 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,13:15], 1, function(x) {mean(x)}))
M_RNase_06 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,16:18], 1, function(x) {mean(x)}))
M_RNase_07 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,19:21], 1, function(x) {mean(x)}))
M_RNase_08 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,22:24], 1, function(x) {mean(x)}))
M_RNase_09 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,25:27], 1, function(x) {mean(x)}))
M_RNase_10 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,28:30], 1, function(x) {mean(x)}))
M_RNase_11 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,31:33], 1, function(x) {mean(x)}))
M_RNase_12 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,34:36], 1, function(x) {mean(x)}))
M_RNase_13 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,37:39], 1, function(x) {mean(x)}))
M_RNase_14 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,40:42], 1, function(x) {mean(x)}))
M_RNase_15 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,43:45], 1, function(x) {mean(x)}))
M_RNase_16 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,46:48], 1, function(x) {mean(x)}))
M_RNase_17 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,49:51], 1, function(x) {mean(x)}))
M_RNase_18 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,52:54], 1, function(x) {mean(x)}))
M_RNase_19 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,55:57], 1, function(x) {mean(x)}))
M_RNase_20 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,58:60], 1, function(x) {mean(x)}))
M_RNase_21 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,61:63], 1, function(x) {mean(x)}))
M_RNase_22 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,64:66], 1, function(x) {mean(x)}))
M_RNase_23 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,67:69], 1, function(x) {mean(x)}))
M_RNase_24 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,70:72], 1, function(x) {mean(x)}))
M_RNase_25 = as.data.frame(apply(RDeeP_HeLa_Interphase_RNase[,73:75], 1, function(x) {mean(x)}))

#create new dataset combining the means for all 25 fractions
Mean_RNase = cbind(M_RNase_01, M_RNase_02, M_RNase_03, M_RNase_04, M_RNase_05, M_RNase_06, M_RNase_07, M_RNase_08, M_RNase_09, M_RNase_10, M_RNase_11, M_RNase_12, M_RNase_13, M_RNase_14, M_RNase_15, M_RNase_16, M_RNase_17, M_RNase_18, M_RNase_19, M_RNase_20, M_RNase_21, M_RNase_22, M_RNase_23, M_RNase_24, M_RNase_25)

colnames(Mean_RNase) <- c('Fraction1_RNase_Mean','Fraction2_RNase_Mean','Fraction3_RNase_Mean','Fraction4_RNase_Mean','Fraction5_RNase_Mean','Fraction6_RNase_Mean','Fraction7_RNase_Mean','Fraction8_RNase_Mean','Fraction9_RNase_Mean','Fraction10_RNase_Mean','Fraction11_RNase_Mean','Fraction12_RNase_Mean','Fraction13_RNase_Mean','Fraction14_RNase_Mean','Fraction15_RNase_Mean','Fraction16_RNase_Mean','Fraction17_RNase_Mean','Fraction18_RNase_Mean','Fraction19_RNase_Mean','Fraction20_RNase_Mean','Fraction21_RNase_Mean','Fraction22_RNase_Mean','Fraction23_RNase_Mean','Fraction24_RNase_Mean','Fraction25_RNase_Mean')

#####repeat for Control dataset

# calculate mean of triplicates for each fraction split into seperate datasets
M_Ctrl_01 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,1:3], 1, function(x) {mean(x)}))
M_Ctrl_02 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,4:6], 1, function(x) {mean(x)}))
M_Ctrl_03 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,7:9], 1, function(x) {mean(x)}))
M_Ctrl_04 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,10:12], 1, function(x) {mean(x)}))
M_Ctrl_05 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,13:15], 1, function(x) {mean(x)}))
M_Ctrl_06 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,16:18], 1, function(x) {mean(x)}))
M_Ctrl_07 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,19:21], 1, function(x) {mean(x)}))
M_Ctrl_08 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,22:24], 1, function(x) {mean(x)}))
M_Ctrl_09 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,25:27], 1, function(x) {mean(x)}))
M_Ctrl_10 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,28:30], 1, function(x) {mean(x)}))
M_Ctrl_11 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,31:33], 1, function(x) {mean(x)}))
M_Ctrl_12 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,34:36], 1, function(x) {mean(x)}))
M_Ctrl_13 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,37:39], 1, function(x) {mean(x)}))
M_Ctrl_14 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,40:42], 1, function(x) {mean(x)}))
M_Ctrl_15 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,43:45], 1, function(x) {mean(x)}))
M_Ctrl_16 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,46:48], 1, function(x) {mean(x)}))
M_Ctrl_17 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,49:51], 1, function(x) {mean(x)}))
M_Ctrl_18 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,52:54], 1, function(x) {mean(x)}))
M_Ctrl_19 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,55:57], 1, function(x) {mean(x)}))
M_Ctrl_20 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,58:60], 1, function(x) {mean(x)}))
M_Ctrl_21 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,61:63], 1, function(x) {mean(x)}))
M_Ctrl_22 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,64:66], 1, function(x) {mean(x)}))
M_Ctrl_23 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,67:69], 1, function(x) {mean(x)}))
M_Ctrl_24 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,70:72], 1, function(x) {mean(x)}))
M_Ctrl_25 = as.data.frame(apply(RDeeP_HeLa_Interphase_Ctrl[,73:75], 1, function(x) {mean(x)}))

#create new dataset combining the means for all 25 fractions
Mean_Ctrl = cbind(M_Ctrl_01, M_Ctrl_02, M_Ctrl_03, M_Ctrl_04, M_Ctrl_05, M_Ctrl_06, M_Ctrl_07, M_Ctrl_08, M_Ctrl_09, M_Ctrl_10, M_Ctrl_11, M_Ctrl_12, M_Ctrl_13, M_Ctrl_14, M_Ctrl_15, M_Ctrl_16, M_Ctrl_17, M_Ctrl_18, M_Ctrl_19, M_Ctrl_20, M_Ctrl_21, M_Ctrl_22, M_Ctrl_23, M_Ctrl_24, M_Ctrl_25)

colnames(Mean_Ctrl) <- c('Fraction1_Ctrl_Mean','Fraction2_Ctrl_Mean','Fraction3_Ctrl_Mean','Fraction4_Ctrl_Mean','Fraction5_Ctrl_Mean','Fraction6_Ctrl_Mean','Fraction7_Ctrl_Mean','Fraction8_Ctrl_Mean','Fraction9_Ctrl_Mean','Fraction10_Ctrl_Mean','Fraction11_Ctrl_Mean','Fraction12_Ctrl_Mean','Fraction13_Ctrl_Mean','Fraction14_Ctrl_Mean','Fraction15_Ctrl_Mean','Fraction16_Ctrl_Mean','Fraction17_Ctrl_Mean','Fraction18_Ctrl_Mean','Fraction19_Ctrl_Mean','Fraction20_Ctrl_Mean','Fraction21_Ctrl_Mean','Fraction22_Ctrl_Mean','Fraction23_Ctrl_Mean','Fraction24_Ctrl_Mean','Fraction25_Ctrl_Mean')

#clearing the Environment of unnecessary data
remove(M_Ctrl_01, M_Ctrl_02, M_Ctrl_03, M_Ctrl_04, M_Ctrl_05, M_Ctrl_06, M_Ctrl_07, M_Ctrl_08, M_Ctrl_09, M_Ctrl_10, M_Ctrl_11, M_Ctrl_12, M_Ctrl_13, M_Ctrl_14, M_Ctrl_15, M_Ctrl_16, M_Ctrl_17, M_Ctrl_18, M_Ctrl_19, M_Ctrl_20, M_Ctrl_21, M_Ctrl_22, M_Ctrl_23, M_Ctrl_24, M_Ctrl_25,
M_RNase_01, M_RNase_02, M_RNase_03, M_RNase_04, M_RNase_05, M_RNase_06, M_RNase_07, M_RNase_08, M_RNase_09, M_RNase_10, M_RNase_11, M_RNase_12, M_RNase_13, M_RNase_14, M_RNase_15, M_RNase_16, M_RNase_17, M_RNase_18, M_RNase_19, M_RNase_20, M_RNase_21, M_RNase_22, M_RNase_23, M_RNase_24, M_RNase_25)

```

#### 1.5 Normalize Rows to 100

This will be done for the Control and RNase Datasets separately:

```{r}
Ctrl_Norm_100 = as.data.frame(sapply(RDeeP_HeLa_Interphase_Ctrl, function(i){(i/apply(RDeeP_HeLa_Interphase_Ctrl,1,sum))*100}))

RNase_Norm_100 = as.data.frame(sapply(RDeeP_HeLa_Interphase_RNase, function(i){(i/apply(RDeeP_HeLa_Interphase_RNase,1,sum))*100}))
```

#### 1.7 Data Exploration, First Graphical Representations

##### Without Normalization
```{r}
plot(1:25, Mean_Ctrl[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CTCF_HUMAN")
lines(1:25, Mean_RNase[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```
```{r}
plot(1:25, Mean_Ctrl[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CY24A_HUMAN")
lines(1:25, Mean_RNase[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```

##### With Normailzation 
```{r}
Mean_Ctrl_Norm_100 = as.data.frame(sapply(Mean_Ctrl, function(i){(i/apply(Mean_Ctrl,1,sum))*100}))

Mean_RNase_Norm_100 = as.data.frame(sapply(Mean_RNase, function(i){(i/apply(Mean_RNase,1,sum))*100}))
```

```{r}
plot(1:25, Mean_Ctrl_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CTCF_HUMAN Normalized", ylim=c(0,25))
lines(1:25, Mean_RNase_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```

```{r}
plot(1:25, Mean_Ctrl_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CY24A_HUMAN Normailzed", ylim=c(0,18))
lines(1:25, Mean_RNase_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```

