---
title: "Topic 3: Proteome-wide Screen for RNA-dependent Proteins; Subtopic 3: HeLa synchronized in Interphase"
author: "Hannah, Johann, Kira, Viktor"
date: "2023-04-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Topic 3: Proteome-wide Screen for RNA-dependent Proteins
#### Subtopic 3: HeLa Cells Synchronized in Interphase

First, we will load the dataset containing the mass spectrometry data from HeLa cells synchronized in interphase:

```{r}
RDeeP_HeLa_Interphase = read.csv("https://www.dropbox.com/s/nm9bgsyg7cv6wu1/RDeeP_HeLa_Interphase.csv?dl=1", header=TRUE, row.names=1, sep = ";")
head(RDeeP_HeLa_Interphase)
```

Are there any missing values in the dataset? 
```{r}
sum(is.na(RDeeP_HeLa_Interphase))
```
Are there any rows that only contain zeros?
```{r}
which(rowSums(RDeeP_HeLa_Interphase)==0)
```
We can also split the dataset into two seperate datasets that contain the Control and RNase values:
```{r}
RDeeP_HeLa_Interphase_Ctrl = cbind(RDeeP_HeLa_Interphase[,1:3],RDeeP_HeLa_Interphase[,7:9],RDeeP_HeLa_Interphase[,13:15],RDeeP_HeLa_Interphase[,19:21],RDeeP_HeLa_Interphase[,25:27],RDeeP_HeLa_Interphase[,31:33],RDeeP_HeLa_Interphase[,37:39],RDeeP_HeLa_Interphase[,43:45],RDeeP_HeLa_Interphase[,49:51],RDeeP_HeLa_Interphase[,55:57],RDeeP_HeLa_Interphase[,61:63],RDeeP_HeLa_Interphase[,67:69],RDeeP_HeLa_Interphase[,73:75],RDeeP_HeLa_Interphase[,79:81],RDeeP_HeLa_Interphase[,85:87],RDeeP_HeLa_Interphase[,91:93],RDeeP_HeLa_Interphase[,97:99],RDeeP_HeLa_Interphase[,103:105],RDeeP_HeLa_Interphase[,109:111],RDeeP_HeLa_Interphase[,115:117],RDeeP_HeLa_Interphase[,121:123],RDeeP_HeLa_Interphase[,127:129],RDeeP_HeLa_Interphase[,133:135],RDeeP_HeLa_Interphase[,139:141],RDeeP_HeLa_Interphase[,145:147])
RDeeP_HeLa_Interphase_RNase=RDeeP_HeLa_Interphase[,-which(names(RDeeP_HeLa_Interphase) %in% colnames(RDeeP_HeLa_Interphase_Ctrl))]
```
```{r}
View(RDeeP_HeLa_Interphase_Ctrl)
View(RDeeP_HeLa_Interphase_RNase)

## ÜBerprüfen welche Reihen in den Datasets nur Nullen enthalten

which(rowSums(RDeeP_HeLa_Interphase_Ctrl)==0)
which(rowSums(RDeeP_HeLa_Interphase_RNase)==0)

## Löschen der Nullreihen im Controldataset


RDeeP_HeLa_Interphase_Ctrl <- RDeeP_HeLa_Interphase_Ctrl[!(rownames(RDeeP_HeLa_Interphase_Ctrl)%in% c("FHOD3_HUMAN","P210L_HUMAN","PKD1_HUMAN","TGM7_HUMAN")),]
View(RDeeP_HeLa_Interphase_Ctrl)
which(rownames(RDeeP_HeLa_Interphase_Ctrl)== "FHOD3_HUMAN")
which(rownames(RDeeP_HeLa_Interphase_Ctrl)== "P210L_HUMAN")

##Löschen der Nullreihen im RNase-Dataset

RDeeP_HeLa_Interphase_RNase <- RDeeP_HeLa_Interphase_RNase[!(rownames(RDeeP_HeLa_Interphase_RNase) %in% c("FHOD3_HUMAN", "KIF1A_HUMANKIF1A_HUMAN")),]
which(rownames(RDeeP_HeLa_Interphase_RNase)== "FHOD3_HUMAN")
which(rownames(RDeeP_HeLa_Interphase_RNase)== "KIF1A_HUMANKIF1A_HUMAN")
```

