---
title: "Topic 3: Proteome-wide Screen for RNA-dependent Proteins; Subtopic 3: HeLa synchronized in Interphase"
author: "Hannah, Johann, Kira, Viktor"
date: "2023-04-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Topic 3: Proteome-wide Screen for RNA-dependent Proteins

#### Subtopic 3: HeLa Cells Synchronized in Interphase

First, we will load the dataset containing the mass spectrometry data from HeLa cells synchronized in interphase:

```{r}
RDeeP_HeLa_Interphase = read.csv("https://www.dropbox.com/s/nm9bgsyg7cv6wu1/RDeeP_HeLa_Interphase.csv?dl=1", header=TRUE, row.names=1, sep = ";")
head(RDeeP_HeLa_Interphase)
```

Are there any missing values in the dataset?

```{r}
sum(is.na(RDeeP_HeLa_Interphase))
```

Are there any rows that only contain zeros?

```{r}
which(rowSums(RDeeP_HeLa_Interphase)==0)
```

#### 1.1 Split Dataset into Control and RNase

We can also split the dataset into two seperate datasets that contain the Control and RNase values:

```{r}
RDeeP_HeLa_Interphase_Ctrl = as.data.frame(
                             # Diese Matrix speichern wir noch als Dataframe
  matrix(
  # Aus dem großen Vektor, den wir mit "unlist" erstellt haben (mit 531450 Einträgen), machen wir eine Matrix mit      7086 Zeilen und 75 Spalten
    
    unlist(
    # Da die untere Schleife einen Dataframe erstellt mit 75 Spalten und drei Zeilen (jede Zelle enthält einen           Vektor, der einer Spalte im originalen Dataframe entspricht), müssen wir aus diesem Dataframe einen einzigen         großen Vektor mit allen Proteineinträgen generieren (das macht der Befehl "unlist")
      
      sapply(seq(0,144,6), function(n) {RDeeP_HeLa_Interphase[,c(1,2,3)+c(n,n,n)]})), 
      # Schleife, die alle Spalten der Control Samples aus dem Dataframe "RDeep_HeLa_Interphase" in Dreier-Grüppchen       (jeweils die drei Replikate pro Fraktion) nacheinander auswählt
    
    nrow=7086, ncol=75))

# Hier werden dem neu erstellten Control Dataframe die Zeilen und Spaltennamen des originalen Dataframes zugeordnet (nutzt die gleiche Schleife zum Auswählen der Control Spalten wie oben)
colnames(RDeeP_HeLa_Interphase_Ctrl) = as.vector(unlist(sapply(seq(0,144,6), function(n) {colnames(RDeeP_HeLa_Interphase[,c(1,2,3)+c(n,n,n)])})))

rownames(RDeeP_HeLa_Interphase_Ctrl) = rownames(RDeeP_HeLa_Interphase)

# Analoges Vorgehen für RNase wie Control, nur, dass sich die Startposition zum Auswählen verändert
RDeeP_HeLa_Interphase_RNase = as.data.frame(matrix(unlist(sapply(seq(0,144,6), function(n) {RDeeP_HeLa_Interphase[,c(4,5,6)+c(n,n,n)]})), nrow=7086, ncol=75))

colnames(RDeeP_HeLa_Interphase_RNase) = as.vector(unlist(sapply(seq(0,144,6), function(n) {colnames(RDeeP_HeLa_Interphase[,c(4,5,6)+c(n,n,n)])})))

rownames(RDeeP_HeLa_Interphase_RNase) = rownames(RDeeP_HeLa_Interphase)
```

#### 1.2 NA Values and Zero Rows
```{r}
## Überprüfen welche Reihen in den Datasets nur Nullen enthalten

which(rowSums(RDeeP_HeLa_Interphase_Ctrl)==0)
which(rowSums(RDeeP_HeLa_Interphase_RNase)==0)

## Löschen der Nullreihen im Controldataset

RDeeP_HeLa_Interphase_Ctrl <- RDeeP_HeLa_Interphase_Ctrl[!(rownames(RDeeP_HeLa_Interphase_Ctrl)%in% c("FHOD3_HUMAN","P210L_HUMAN","PKD1_HUMAN","TGM7_HUMAN","KIF1A_HUMAN")),]

##Löschen der Nullreihen im RNase-Dataset

RDeeP_HeLa_Interphase_RNase <- RDeeP_HeLa_Interphase_RNase[!(rownames(RDeeP_HeLa_Interphase_RNase) %in% c("FHOD3_HUMAN","P210L_HUMAN","PKD1_HUMAN","TGM7_HUMAN", "KIF1A_HUMAN")),]
```

#### 1.4 Mean of Replicates

```{r}
Mean_Ctrl = as.data.frame(
            # Abspeichern als Dataframe
  
  sapply(seq(0,72,3), function(i) {
  # Äußere Schleife, die zum Auswählen der drei Replikate pro Fraktion da ist (Startvektor c(1,2,3) wird jeweils um c(3,3,3) erhöht) 
    
    apply(RDeeP_HeLa_Interphase_Ctrl[,c(1,2,3)+c(i,i,i)], 1, function(x) {mean(x)})
    # Innere Schleife, die nachdem die drei Replikate für eine Fraktion ausgewählt wurden, über alle Zeilen dieser       Replikate den Mittelwert berechnet
    
    }))

# Erstellen neuer Spaltennamen für den Mean_Ctrl Dataframe. Der Befehl "paste" erlaubt es, sowohl Text als auch Befehle als ein String zu haben (sep="", bedeutet, dass die Elemente durch kein Leerzeichen voneinander getrennt werden sollen)
colnames(Mean_Ctrl) = paste("Fraction",seq(1,25,1),"_Ctrl_Mean",sep="")

# Analoges Vorgehen für den RNase Dataframe
Mean_RNase = as.data.frame(
  sapply(seq(0,72,3), function(i) {
    apply(RDeeP_HeLa_Interphase_RNase[,c(1,2,3)+c(i,i,i)], 1, function(x) {mean(x)})
    }))

colnames(Mean_RNase) = paste("Fraction",seq(1,25,1),"_RNase_Mean",sep="")
```


#### 1.5 Normalize Rows to 100

This will be done for the Control and RNase Datasets separately:

```{r}
Ctrl_Norm_100 = as.data.frame(sapply(RDeeP_HeLa_Interphase_Ctrl, function(i){(i/apply(RDeeP_HeLa_Interphase_Ctrl,1,sum))*100}))

RNase_Norm_100 = as.data.frame(sapply(RDeeP_HeLa_Interphase_RNase, function(i){(i/apply(RDeeP_HeLa_Interphase_RNase,1,sum))*100}))
```

#### 1.7 Data Exploration, First Graphical Representations

##### Without Normalization
```{r}
plot(1:25, Mean_Ctrl[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CTCF_HUMAN")
lines(1:25, Mean_RNase[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```
```{r}
plot(1:25, Mean_Ctrl[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CY24A_HUMAN")
lines(1:25, Mean_RNase[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```

##### With Normailzation 
```{r}
Mean_Ctrl_Norm_100 = as.data.frame(sapply(Mean_Ctrl, function(i){(i/apply(Mean_Ctrl,1,sum))*100}))

Mean_RNase_Norm_100 = as.data.frame(sapply(Mean_RNase, function(i){(i/apply(Mean_RNase,1,sum))*100}))
```

```{r}
plot(1:25, Mean_Ctrl_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CTCF_HUMAN Normalized", ylim=c(0,25))
lines(1:25, Mean_RNase_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```

```{r}
plot(1:25, Mean_Ctrl_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CY24A_HUMAN Normailzed", ylim=c(0,18))
lines(1:25, Mean_RNase_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```

### Smoothing and Determination of Maxima

#### 2.1 Smoothing the Data

We will smooth out the Data by calculating the mean value for each fraction within a defined neighborhood (n = 1):
```{r}
# n = 1 (left and right neighbor)
Mean_Ctrl_Smooth = 
  # 5: Abspeichern der Matrix als Data.Frame
  as.data.frame(
# 4: Spaltenweises Verbinden der zwei Vektoren und der Matrix | Output: Matrix mit 25 Spalten und 7081 Zeilen 
cbind(
  
  # 2: Mittelwert-Berechnung für die Fraktion 1 (Mittelwert aus der Fraktion 1 und 2) | Output: Vektor mit 7081        Einträgen
  (Mean_Ctrl[,1]+Mean_Ctrl[,2])/2,
      
      # 1: Schleife, die jeweils ein Fenster aus 3 Fraktionen auswählt (startet bei 1,2,3 und endet bei 23,24,25) und       dann mit einer zweiten Schleife den Mittelwert dieser 3 Fraktione über alle Reihen berechnet | Output: Matrix        mit 23 Spalten und 7081 Zeilen, die die Mittelwerte für die Fraktionen 2 bis 24 enthält
      sapply(seq(0,22,1), function(i) {apply(Mean_Ctrl[,c(1,2,3)+c(i,i,i)], 1, function(x) {mean(x)})}), 
  
  # 3: Mittelwert-Berechnung für die Fraktion 25 (Mittelwert aus der Fraktion 24 und 25) | Output: Vektor mit 7081     Einträgen
  (Mean_Ctrl[,24]+Mean_Ctrl[,25])/2)
)

colnames(Mean_Ctrl_Smooth) = colnames(Mean_Ctrl)


# Gleicher Code für RNase
Mean_RNase_Smooth = 
  as.data.frame(
cbind(Mean_RNase[,1],
      sapply(seq(0,22,1), function(i) {apply(Mean_RNase[,c(1,2,3)+c(i,i,i)], 1, function(x) {mean(x)})}), 
      Mean_RNase[,25])
)

colnames(Mean_RNase_Smooth) = colnames(Mean_RNase)
```

We will now normalize this data in a way, that the sum of each row will equal 100:
```{r}
Mean_Ctrl_Smooth_Norm_100 = as.data.frame(sapply(Mean_Ctrl_Smooth, function(i){(i/apply(Mean_Ctrl_Smooth,1,sum))*100}))

Mean_RNase_Smooth_Norm_100 = as.data.frame(sapply(Mean_RNase_Smooth, function(i){(i/apply(Mean_RNase_Smooth,1,sum))*100}))
```

Now let us explore how this Smoothing and Normalization effects the data distribution:
```{r}
plot(1:25, Mean_Ctrl [which(rownames(Mean_Ctrl)==c("CTCF_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CTCF_HUMAN", ylim=c(0,2200000))
lines(1:25, Mean_RNase[which(rownames(Mean_Ctrl)==c("CTCF_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)

plot(1:25, Mean_Ctrl_Smooth[which(rownames(Mean_Ctrl)==c("CTCF_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CTCF_HUMAN (Smoothed)", ylim=c(0,2200000))
lines(1:25, Mean_RNase_Smooth[which(rownames(Mean_Ctrl)==c("CTCF_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)

plot(1:25, Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==c("CTCF_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CTCF_HUMAN (Smoothed and Normalized)", ylim=c(0,22))
lines(1:25, Mean_RNase_Smooth_Norm_100[which(rownames(Mean_Ctrl)==c("CTCF_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```

```{r}
plot(1:25, Mean_Ctrl [which(rownames(Mean_Ctrl)==c("CY24A_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CY24A_HUMAN", ylim=c(0,950000))
lines(1:25, Mean_RNase[which(rownames(Mean_Ctrl)==c("CY24A_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)

plot(1:25, Mean_Ctrl_Smooth[which(rownames(Mean_Ctrl)==c("CY24A_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CY24A_HUMAN (Smoothed)", ylim=c(0,950000))
lines(1:25, Mean_RNase_Smooth[which(rownames(Mean_Ctrl)==c("CY24A_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)

plot(1:25, Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==c("CY24A_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CY24A_HUMAN (Smoothed and Normalized)", ylim=c(0,22))
lines(1:25, Mean_RNase_Smooth_Norm_100[which(rownames(Mean_Ctrl)==c("CY24A_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```
```{r}
plot(1:25, Mean_Ctrl [which(rownames(Mean_Ctrl)==c("ABCA1_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="ABCA1_HUMAN", ylim=c(0,220000))
lines(1:25, Mean_RNase[which(rownames(Mean_Ctrl)==c("ABCA1_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)

plot(1:25, Mean_Ctrl_Smooth[which(rownames(Mean_Ctrl)==c("ABCA1_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="ABCA1_HUMAN (Smoothed)", ylim=c(0,220000))
lines(1:25, Mean_RNase_Smooth[which(rownames(Mean_Ctrl)==c("ABCA1_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)

plot(1:25, Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==c("ABCA1_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="ABCA1_HUMAN (Smoothed and Normalized)", ylim=c(0,38))
lines(1:25, Mean_RNase_Smooth_Norm_100[which(rownames(Mean_Ctrl)==c("ABCA1_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```


#### 2.2 Determination of Global and Local Maxima

##### Global Maxima

Let us first start with the global maxima: we want a code that tells us the global maximum fraction position for each gene and condition (Control and RNase).
We can calculate the global maxima by asking the question: "Which Protein Fractions contains the maximum protein amount?"
```{r}
Mean_Ctrl_Gbl_Max = 
  
  # 2: Abspeichern als Matrix (besser für weiter Berechnungen (siehe unten))
  as.matrix(
    
    # 1: Schleife, die für jedes Gen des Datensatzes "Mean_Ctrl_Smooth_Norm_100" bestimmt, welche Fraktion den           größten Protein-Anteil enthält | Output: Liste mit allen Fraktionen mit größtem Protein-Anteil pro Gen             (Problem: manchmal mehrere Einträge für ein Gen (siehe Plot von Gen ABCA1_HUMAN oben))
    sapply(seq(1, nrow(RDeeP_HeLa_Interphase_Ctrl), 1), function(i) {which(Mean_Ctrl_Smooth_Norm_100[i,] == max(Mean_Ctrl_Smooth_Norm_100[i,]))}))


## If 2 fraction positions contain the maximum protein amount, we determine the mean of these 2 fraction positions

# 2: Wir rufen die Fraction Positions für die Zeilen ab, die genau zwei globale Maxima enthalten | Output: Liste mit den globalen Maxima für alle Gene
Mean_Ctrl_Gbl_Max[
  
  # 1: Für jedes Gen wird geschaut, wie viele Einträge es für die globalen Maxima gibt und verglichen, ob es genau 2   Einträge gibt. "which()" gibt dann die Gene aus, für die diese Bedingung TRUE ist. | Output: vektor aller Zeilen,    für die Bedingung stimmt.
  which(
    sapply(seq(1,nrow(RDeeP_HeLa_Interphase_Ctrl),1),function(i) {
      length(which(Mean_Ctrl_Smooth_Norm_100[i,] == max(Mean_Ctrl_Smooth_Norm_100[i,])))}) == 2), 
     
     # 3: Wir ersetzen jede Zeile, die 2 Einträge besitzt, mit dem Mittelwert aus diesen 2 Einträgen
  1] = 
  apply(matrix(unlist(Mean_Ctrl_Gbl_Max[which(sapply(seq(1,nrow(RDeeP_HeLa_Interphase_Ctrl),1),function(i) {length(which(Mean_Ctrl_Smooth_Norm_100[i,] == max(Mean_Ctrl_Smooth_Norm_100[i,]) ))}) == 2),1]), ncol=2, byrow=T), 1, function(x) {mean(x)})

## If 3 fraction positions contain the maximum protein amount, we determine the mean of these 3 fraction positions
Mean_Ctrl_Gbl_Max[which(sapply(seq(1,nrow(RDeeP_HeLa_Interphase_Ctrl),1),function(i) {length(which(Mean_Ctrl_Smooth_Norm_100[i,] == max(Mean_Ctrl_Smooth_Norm_100[i,]) ))}) == 3),1] = apply(matrix(unlist(Mean_Ctrl_Gbl_Max[which(sapply(seq(1,nrow(RDeeP_HeLa_Interphase_Ctrl),1),function(i) {length(which(Mean_Ctrl_Smooth_Norm_100[i,] == max(Mean_Ctrl_Smooth_Norm_100[i,]) ))}) == 3),1]), ncol=3, byrow=T), 1, function(x) {mean(x)})

colnames(Mean_Ctrl_Gbl_Max) = c("Ctrl_Gbl_Max")
rownames(Mean_Ctrl_Gbl_Max) = rownames(Mean_Ctrl_Smooth_Norm_100)


Mean_RNase_Gbl_Max = as.matrix(sapply(seq(1,nrow(RDeeP_HeLa_Interphase_RNase),1),function(i) {which(Mean_RNase_Smooth_Norm_100[i,] == max(Mean_RNase_Smooth_Norm_100[i,]))}))

Mean_RNase_Gbl_Max[which(sapply(seq(1,nrow(RDeeP_HeLa_Interphase_RNase),1),function(i) {length(which(Mean_RNase_Smooth_Norm_100[i,] == max(Mean_RNase_Smooth_Norm_100[i,]) ))}) == 2),1] = apply(matrix(unlist(Mean_RNase_Gbl_Max[which(sapply(seq(1,nrow(RDeeP_HeLa_Interphase_RNase),1),function(i) {length(which(Mean_RNase_Smooth_Norm_100[i,] == max(Mean_RNase_Smooth_Norm_100[i,]) ))}) == 2),1]), ncol=2, byrow=T), 1, function(x) {mean(x)})

Mean_RNase_Gbl_Max[which(sapply(seq(1,nrow(RDeeP_HeLa_Interphase_RNase),1),function(i) {length(which(Mean_RNase_Smooth_Norm_100[i,] == max(Mean_RNase_Smooth_Norm_100[i,]) ))}) == 3),1] = apply(matrix(unlist(Mean_RNase_Gbl_Max[which(sapply(seq(1,nrow(RDeeP_HeLa_Interphase_RNase),1),function(i) {length(which(Mean_RNase_Smooth_Norm_100[i,] == max(Mean_RNase_Smooth_Norm_100[i,]) ))}) == 3),1]), ncol=3, byrow=T), 1, function(x) {mean(x)})

colnames(Mean_RNase_Gbl_Max) = c("RNase_Gbl_Max")
rownames(Mean_RNase_Gbl_Max) = rownames(Mean_RNase_Smooth_Norm_100)

Mean_Gbl_Max = cbind(Mean_Ctrl_Gbl_Max, Mean_RNase_Gbl_Max)

# length(which(unlist(Mean_Gbl_Max[,1]) == unlist(Mean_Gbl_Max[,2])))
# length(which(abs(unlist(Mean_Gbl_Max[,1])-unlist(Mean_Gbl_Max[,2])) >= 2))
```


Let us see if it worked!
```{r}
gene.name=c("CTCF_HUMAN")

plot(1:25, Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main=paste(paste(gene.name, "(Smoothed and Normalized)")), ylim=c(0,25))

abline(v=Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),],lwd=3,col="green",lty=2)

lines(1:25, Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name),], type="l",lwd=3,col="red")

abline(v=Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),],lwd=3,col="red",lty=3)

grid()

legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
rm(gene.name)
```


```{r}
gene.name=c("CY24A_HUMAN")

plot(1:25, Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main=paste(paste(gene.name, "(Smoothed and Normalized)")), ylim=c(0,20))

abline(v=Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),],lwd=3,col="green",lty=2)

lines(1:25, Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name),], type="l",lwd=3,col="red")

abline(v=Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),],lwd=3,col="red",lty=3)

grid()

legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
rm(gene.name)
```
But Smoothing sometimes changes the position of the maxima!!!!

```{r}
gene.name=c("RS29_HUMAN")

plot(1:25, Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main=paste(paste(gene.name, "(Smoothed and Normalized)")), ylim=c(0,25))

abline(v=Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),],lwd=3,col="green",lty=2)

lines(1:25, Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name),], type="l",lwd=3,col="red")

abline(v=Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),],lwd=3,col="red",lty=3)

grid()

legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)


plot(1:25, Mean_Ctrl_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==gene.name),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main=paste(paste(gene.name, "(Normalized)")), ylim=c(0,25))

abline(v=Mean_Ctrl_Gbl_Max[which(rownames(RDeeP_HeLa_Interphase)==gene.name),],lwd=3,col="green",lty=3)

lines(1:25, Mean_RNase_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==gene.name),], type="l",lwd=3,col="red")

abline(v=Mean_RNase_Gbl_Max[which(rownames(RDeeP_HeLa_Interphase)==gene.name),],lwd=3,col="red",lty=3)

grid()

legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
rm(gene.name)
```
Another Example, where the peak positions would be at the same fraction position in the unsmoothed data but differ in the smoothen data:
```{r}
gene.name="XXLT1_HUMAN"

plot(1:25, Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),],type="l",lwd=3,col="green",xlab="Protein Fractions",ylab="Relative Protein Amount",main=paste(paste(gene.name, "(Smoothed and Normalized)")), ylim=c(0,max(max(Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),]), max(Mean_RNase_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),]))+3))

abline(v=Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),],lwd=3,col="green",lty=3)

lines(1:25, Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name),], type="l",lwd=3,col="red")

abline(v=Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),],lwd=3,col="red",lty=3)

grid()

legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)


plot(1:25, Mean_Ctrl_Norm_100[which(rownames(Mean_Ctrl)==gene.name),],type="l",lwd=3,col="green",xlab="Protein Fractions",ylab="Relative Protein Amount",main=paste(paste(gene.name, "(Normalized)")), ylim=c(0,max(max(Mean_Ctrl_Norm_100[which(rownames(Mean_Ctrl)==gene.name),]), max(Mean_RNase_Norm_100[which(rownames(Mean_Ctrl)==gene.name),]))+3))

abline(v=Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),],lwd=3,col="green",lty=3)

lines(1:25, Mean_RNase_Norm_100[which(rownames(Mean_RNase)==gene.name),], type="l",lwd=3,col="red")

abline(v=Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),],lwd=3,col="red",lty=3)

grid()

legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)

rm(gene.name)
```
##### Local Maxima

We will now calculate the fraction positions of all local maxima for every gene and condition. But what defines a local maximum? 
We will look at the protein amount for a neighborhood of n = 2 for each fraction positions (for local maxima at the edges we will use slightly different criteria):

X X [X] X X 

We will then compare the protein amount in that fraction position to the protein amount for the 4 fraction positions around that fraction position and ask the question: Is the protein amount in that fraction greater or equal to its neighborhood? If TRUE then we define that fraction position as a local maximum.
```{r}
Mean_Ctrl_Loc_Max = as.data.frame(matrix(NA, nrow = nrow(RDeeP_HeLa_Interphase_Ctrl), ncol = 25))

Fra.Pos = sapply(seq(0,20,1), function(i) {which(seq(2*nrow(RDeeP_HeLa_Interphase_Ctrl)+1,3*nrow(RDeeP_HeLa_Interphase_Ctrl),1) %in% which(apply(Mean_Ctrl_Smooth_Norm_100[,c(1:5)+c(i,i,i,i,i)], 1, function(x) {max(x)}) == Mean_Ctrl_Smooth_Norm_100[,c(1:5)+c(i,i,i,i,i)] & apply(Mean_Ctrl_Smooth_Norm_100[,c(1:5)+c(i,i,i,i,i)], 1, function(x) {max(x)}) != 0))})

Mean_Ctrl_Loc_Max[, 3:23] = sapply(seq(1,21,1), function(n) {
  replace(
        Mean_Ctrl_Loc_Max[, n+2], 
        Fra.Pos[[n]], 
        n+2)})

rownames(Mean_Ctrl_Loc_Max) = rownames(Mean_Ctrl)
colnames(Mean_Ctrl_Loc_Max) = colnames(Mean_Ctrl)



Mean_RNase_Loc_Max = as.data.frame(matrix(NA, nrow = nrow(RDeeP_HeLa_Interphase_RNase), ncol = 25))

Fra.Pos = sapply(seq(0,20,1), function(i) {which(seq(2*nrow(RDeeP_HeLa_Interphase_RNase)+1,3*nrow(RDeeP_HeLa_Interphase_RNase),1) %in% which(apply(Mean_RNase_Smooth_Norm_100[,c(1:5)+c(i,i,i,i,i)], 1, function(x) {max(x)}) == Mean_RNase_Smooth_Norm_100[,c(1:5)+c(i,i,i,i,i)] & apply(Mean_RNase_Smooth_Norm_100[,c(1:5)+c(i,i,i,i,i)], 1, function(x) {max(x)}) != 0))})

Mean_RNase_Loc_Max[, 3:23] = sapply(seq(1,21,1), function(n) {
  replace(
        Mean_RNase_Loc_Max[, n+2], 
        Fra.Pos[[n]], 
        n+2)})

rownames(Mean_RNase_Loc_Max) = rownames(Mean_RNase)
colnames(Mean_RNase_Loc_Max) = colnames(Mean_RNase)


## Edge Cases:

# Fraction 1
Mean_Ctrl_Loc_Max[which(Mean_Ctrl_Smooth_Norm_100[,1] >= Mean_Ctrl_Smooth_Norm_100[,2] & Mean_Ctrl_Smooth_Norm_100[,1] >= Mean_Ctrl_Smooth_Norm_100[,3] & Mean_Ctrl_Smooth_Norm_100[,1] != 0),1] = 1

Mean_RNase_Loc_Max[which(Mean_RNase_Smooth_Norm_100[,1] >= Mean_RNase_Smooth_Norm_100[,2] & Mean_RNase_Smooth_Norm_100[,1] >= Mean_RNase_Smooth_Norm_100[,3] & Mean_RNase_Smooth_Norm_100[,1] != 0),1] = 1

# Fraction 2
Mean_Ctrl_Loc_Max[which(Mean_Ctrl_Smooth_Norm_100[,2] >= Mean_Ctrl_Smooth_Norm_100[,3] & Mean_Ctrl_Smooth_Norm_100[,2] >= Mean_Ctrl_Smooth_Norm_100[,4] & Mean_Ctrl_Smooth_Norm_100[,2] >= Mean_Ctrl_Smooth_Norm_100[,1] & Mean_Ctrl_Smooth_Norm_100[,1] != 0), 2] = 2

Mean_RNase_Loc_Max[which(Mean_RNase_Smooth_Norm_100[,2] >= Mean_RNase_Smooth_Norm_100[,3] & Mean_RNase_Smooth_Norm_100[,2] >= Mean_RNase_Smooth_Norm_100[,4] & Mean_RNase_Smooth_Norm_100[,2] >= Mean_RNase_Smooth_Norm_100[,1] & Mean_RNase_Smooth_Norm_100[,1] != 0), 2] = 2

# Fraction 25
Mean_Ctrl_Loc_Max[which(Mean_Ctrl_Smooth_Norm_100[,25] >= Mean_Ctrl_Smooth_Norm_100[,24] & Mean_Ctrl_Smooth_Norm_100[,25] >= Mean_Ctrl_Smooth_Norm_100[,23] & Mean_Ctrl_Smooth_Norm_100[,25] != 0), 25] = 25

Mean_RNase_Loc_Max[which(Mean_RNase_Smooth_Norm_100[,25] >= Mean_RNase_Smooth_Norm_100[,24] & Mean_RNase_Smooth_Norm_100[,25] >= Mean_RNase_Smooth_Norm_100[,23] & Mean_RNase_Smooth_Norm_100[,25] != 0), 25] = 25

# Fraction 24
Mean_Ctrl_Loc_Max[which(Mean_Ctrl_Smooth_Norm_100[,24] >= Mean_Ctrl_Smooth_Norm_100[,23] & Mean_Ctrl_Smooth_Norm_100[,24] >= Mean_Ctrl_Smooth_Norm_100[,22] & Mean_Ctrl_Smooth_Norm_100[,24] >= Mean_Ctrl_Smooth_Norm_100[,25] & Mean_Ctrl_Smooth_Norm_100[,24] != 0), 24] = 24

Mean_RNase_Loc_Max[which(Mean_RNase_Smooth_Norm_100[,24] >= Mean_RNase_Smooth_Norm_100[,23] & Mean_RNase_Smooth_Norm_100[,24] >= Mean_RNase_Smooth_Norm_100[,22] & Mean_RNase_Smooth_Norm_100[,24] >= Mean_RNase_Smooth_Norm_100[,25] & Mean_RNase_Smooth_Norm_100[,24] != 0), 24] = 24


## Removal of Global Maxima in Local Maxima Datasets (also removes all double and triple global maxima!!!)

Crtl_Mask = matrix(1, nrow = nrow(RDeeP_HeLa_Interphase_Ctrl)*25, ncol = 1)

Crtl_Mask[which(apply(Mean_Ctrl_Smooth_Norm_100, 1, function(x) {max(x)}) == Mean_Ctrl_Smooth_Norm_100)] = NA

Crtl_Mask = as.data.frame(matrix(unlist(Crtl_Mask), nrow=nrow(RDeeP_HeLa_Interphase_Ctrl), ncol=25))

Mean_Ctrl_Loc_Max = Mean_Ctrl_Loc_Max * Crtl_Mask

rm(Crtl_Mask)


RNase_Mask = matrix(1, nrow = nrow(RDeeP_HeLa_Interphase_RNase)*25, ncol = 1)

RNase_Mask[which(apply(Mean_RNase_Smooth_Norm_100, 1, function(x) {max(x)}) == Mean_RNase_Smooth_Norm_100)] = NA

RNase_Mask = as.data.frame(matrix(unlist(RNase_Mask), nrow=nrow(RDeeP_HeLa_Interphase_RNase), ncol=25))

Mean_RNase_Loc_Max = Mean_RNase_Loc_Max * RNase_Mask

rm(RNase_Mask)


### Combine double and triple peaks into single peaks

## Double peaks
Fra.Pos = sapply(seq(0,21,1), function(i) {which(!(is.na(Mean_Ctrl_Loc_Max[,c(2)+c(i)])) & !(is.na(Mean_Ctrl_Loc_Max[,c(3)+c(i)])) & is.na(Mean_Ctrl_Loc_Max[,c(1)+c(i)]) & is.na(Mean_Ctrl_Loc_Max[,c(4)+c(i)]))})

Mean_Ctrl_Loc_Max[, 2:23] = sapply(seq(1,22,1), function(n) {
  replace(
        Mean_Ctrl_Loc_Max[, n+1], 
        Fra.Pos[[n]], 
        n+1.5)})

Mean_Ctrl_Loc_Max[, 3:24] = sapply(seq(1,22,1), function(n) {
  replace(
        Mean_Ctrl_Loc_Max[, n+2], 
        Fra.Pos[[n]], 
        NA)})

## Edge Cases (not necessary in this case)

# Fra.Pos = which(!(is.na(Mean_Ctrl_Loc_Max[,c(1)])) & !(is.na(Mean_Ctrl_Loc_Max[,c(2)])) & !(!(is.na(Mean_Ctrl_Loc_Max[,c(1)])) & !(is.na(Mean_Ctrl_Loc_Max[,c(2)])) & !(is.na(Mean_Ctrl_Loc_Max[,c(3)]))))

# Mean_Ctrl_Loc_Max[Fra.Pos[[1]],1]=1.5
# Mean_Ctrl_Loc_Max[Fra.Pos[[1]],2]=NA

# Fra.Pos = which(!(is.na(Mean_Ctrl_Loc_Max[,c(24)])) & !(is.na(Mean_Ctrl_Loc_Max[,c(25)])) & !(!(is.na(Mean_Ctrl_Loc_Max[,c(23)])) & !(is.na(Mean_Ctrl_Loc_Max[,c(24)])) & !(is.na(Mean_Ctrl_Loc_Max[,c(25)]))))

# Mean_Ctrl_Loc_Max[Fra.Pos[[1]],24]=24.5
# Mean_Ctrl_Loc_Max[Fra.Pos[[1]],25]=NA


Fra.Pos = sapply(seq(0,21,1), function(i) {which(!(is.na(Mean_RNase_Loc_Max[,c(2)+c(i)])) & !(is.na(Mean_RNase_Loc_Max[,c(3)+c(i)])) & is.na(Mean_RNase_Loc_Max[,c(1)+c(i)]) & is.na(Mean_RNase_Loc_Max[,c(4)+c(i)]))})

Mean_RNase_Loc_Max[, 2:23] = sapply(seq(1,22,1), function(n) {
  replace(
        Mean_RNase_Loc_Max[, n+1], 
        Fra.Pos[[n]], 
        n+1.5)})

Mean_RNase_Loc_Max[, 3:24] = sapply(seq(1,22,1), function(n) {
  replace(
        Mean_RNase_Loc_Max[, n+2], 
        Fra.Pos[[n]], 
        NA)})

# Edge Cases (not necessary in this case)

# Fra.Pos = which(!(is.na(Mean_RNase_Loc_Max[,c(1)])) & !(is.na(Mean_RNase_Loc_Max[,c(2)])) & !(!(is.na(Mean_RNase_Loc_Max[,c(1)])) & !(is.na(Mean_RNase_Loc_Max[,c(2)])) & !(is.na(Mean_RNase_Loc_Max[,c(3)]))))

# Mean_RNase_Loc_Max[Fra.Pos[[1]],1]=1.5
# Mean_RNase_Loc_Max[Fra.Pos[[1]],2]=NA

# Fra.Pos = which(!(is.na(Mean_RNase_Loc_Max[,c(24)])) & !(is.na(Mean_RNase_Loc_Max[,c(25)])) & !(!(is.na(Mean_RNase_Loc_Max[,c(23)])) & !(is.na(Mean_RNase_Loc_Max[,c(24)])) & !(is.na(Mean_RNase_Loc_Max[,c(25)]))))

# Mean_RNase_Loc_Max[Fra.Pos[[1]],24]=24.5
# Mean_RNase_Loc_Max[Fra.Pos[[1]],25]=NA



# Triple peaks
Fra.Pos = sapply(seq(0,22,1), function(i) {which(!(is.na(Mean_Ctrl_Loc_Max[,c(1)+c(i)])) & !(is.na(Mean_Ctrl_Loc_Max[,c(2)+c(i)])) & !(is.na(Mean_Ctrl_Loc_Max[,c(3)+c(i)])))})

Mean_Ctrl_Loc_Max[, 1:23] = sapply(seq(1,23,1), function(n) {
  replace(
        Mean_Ctrl_Loc_Max[, n], 
        Fra.Pos[[n]], 
        NA)})

Mean_Ctrl_Loc_Max[, 3:25] = sapply(seq(1,23,1), function(n) {
  replace(
        Mean_Ctrl_Loc_Max[, n+2], 
        Fra.Pos[[n]], 
        NA)})


Fra.Pos = sapply(seq(0,22,1), function(i) {which(!(is.na(Mean_RNase_Loc_Max[,c(1)+c(i)])) & !(is.na(Mean_RNase_Loc_Max[,c(2)+c(i)])) & !(is.na(Mean_RNase_Loc_Max[,c(3)+c(i)])))})

Mean_RNase_Loc_Max[, 1:23] = sapply(seq(1,23,1), function(n) {
  replace(
        Mean_RNase_Loc_Max[, n], 
        Fra.Pos[[n]], 
        NA)})

Mean_RNase_Loc_Max[, 3:25] = sapply(seq(1,23,1), function(n) {
  replace(
        Mean_RNase_Loc_Max[, n+2], 
        Fra.Pos[[n]], 
        NA)})


rm(Fra.Pos)
```


Did it work? Let us look at the examples from before!
```{r}
gene.name="CTCF_HUMAN"

par(mar=c(5, 4, 4, 7), xpd=F)

plot(1:25, Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),],type="l",lwd=3,col="green",xlab="Protein Fractions",ylab="Relative Protein Amount",main=paste(paste(gene.name, "(Smoothed and Normalized)")), ylim=c(0,max(max(Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),]), max(Mean_RNase_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),]))+3))

grid()

segments(unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),]), 
         -1, 
         unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),]), 
         Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name), unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),])], 
         lwd=3,col="green",lty=2)

if(!is.null(unlist(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]))) {

segments(unlist(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]), 
         -1, 
         unlist(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]), 
         unlist(Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name), which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]), 
         lwd=3,col="green",lty=2)}

lines(1:25, Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name),], type="l",lwd=3,col="red")

segments(unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),]), 
         -1, 
         unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),]), 
         Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name), unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),])], 
         lwd=3,col="red",lty=3)

if(!is.null(unlist(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]))) {

segments(unlist(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]), 
         -1, 
         unlist(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]), 
         unlist(Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name), which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]), 
         lwd=3,col="red",lty=3)}

points(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name), ], Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),])], pch=21, col="black", bg="green", cex=1.5)

points(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))], Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name), which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))], pch=24, col="black", bg="green", cex=1.2)

points(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name), ], Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name),unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),])], pch=21, col="black", bg="red", cex=1.5)

points(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))], Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name), which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))], pch=24, col="black", bg="red", cex=1.2)

par(xpd=T)

legend("topright",inset = c(-0.23,0), legend=c("Control","RNase", "Global", "Local"), pch=c(NA, NA, 21, 24), lty=c(1,1,NA,NA), col=c("green","red","black","black"), lwd = c(2,2,1.5,1.5))

rm(gene.name)
```
```{r}
gene.name="CY24A_HUMAN"

par(mar=c(5, 4, 4, 7), xpd=F)

plot(1:25, Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),],type="l",lwd=3,col="green",xlab="Protein Fractions",ylab="Relative Protein Amount",main=paste(paste(gene.name, "(Smoothed and Normalized)")), ylim=c(0,max(max(Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),]), max(Mean_RNase_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),]))+3))

grid()

segments(unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),]), 
         -1, 
         unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),]), 
         Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name), unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),])], 
         lwd=3,col="green",lty=2)

if(!is.null(unlist(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]))) {

segments(unlist(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]), 
         -1, 
         unlist(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]), 
         unlist(Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name), which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]), 
         lwd=3,col="green",lty=2)}

lines(1:25, Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name),], type="l",lwd=3,col="red")

segments(unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),]), 
         -1, 
         unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),]), 
         Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name), unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),])], 
         lwd=3,col="red",lty=3)

if(!is.null(unlist(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]))) {

segments(unlist(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]), 
         -1, 
         unlist(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]), 
         unlist(Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name), which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]), 
         lwd=3,col="red",lty=3)}

points(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name), ], Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),])], pch=21, col="black", bg="green", cex=1.5)

points(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))], Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name), which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))], pch=24, col="black", bg="green", cex=1.2)

points(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name), ], Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name),unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),])], pch=21, col="black", bg="red", cex=1.5)

points(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))], Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name), which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))], pch=24, col="black", bg="red", cex=1.2)

par(xpd=T)

legend("topright",inset = c(-0.23,0), legend=c("Control","RNase", "Global", "Local"), pch=c(NA, NA, 21, 24), lty=c(1,1,NA,NA), col=c("green","red","black","black"), lwd = c(2,2,1.5,1.5))

rm(gene.name)
```



#### 2.Extra: Automatic Graph Plotter
```{r}
# RL32_HUMAN
# ABCA1_HUMAN (gut für triple peaks to single peak)
# NAT10_HUMAN (gut für verschiedene lokale Peaks)
gene.name="NAT10_HUMAN"

par(mar=c(5, 4, 4, 7), xpd=F)

plot(1:25, Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),],type="l",lwd=3,col="green",xlab="Protein Fractions",ylab="Relative Protein Amount",main=paste(paste(gene.name, "(Smoothed and Normalized)")), ylim=c(0,max(max(Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),]), max(Mean_RNase_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),]))+3))

grid()

segments(unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),]), 
         -1, 
         unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),]), 
         Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name), unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),])], 
         lwd=3,col="green",lty=2)

if(!is.null(unlist(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]))) {

segments(unlist(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]), 
         -1, 
         unlist(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]), 
         unlist(Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name), which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))]), 
         lwd=3,col="green",lty=2)}

lines(1:25, Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name),], type="l",lwd=3,col="red")

segments(unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),]), 
         -1, 
         unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),]), 
         Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name), unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),])], 
         lwd=3,col="red",lty=3)

if(!is.null(unlist(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]))) {

segments(unlist(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]), 
         -1, 
         unlist(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]), 
         unlist(Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name), which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))]), 
         lwd=3,col="red",lty=3)}

points(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name), ], Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name),unlist(Mean_Ctrl_Gbl_Max[which(rownames(Mean_Ctrl)==gene.name),])], pch=21, col="black", bg="green", cex=1.5)

points(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))], Mean_Ctrl_Smooth_Norm_100[which(rownames(Mean_Ctrl)==gene.name), which(!is.na(Mean_Ctrl_Loc_Max[which(rownames(Mean_Ctrl)==gene.name),]))], pch=24, col="black", bg="green", cex=1.2)

points(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name), ], Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name),unlist(Mean_RNase_Gbl_Max[which(rownames(Mean_RNase)==gene.name),])], pch=21, col="black", bg="red", cex=1.5)

points(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))], Mean_RNase_Smooth_Norm_100[which(rownames(Mean_RNase)==gene.name), which(!is.na(Mean_RNase_Loc_Max[which(rownames(Mean_RNase)==gene.name),]))], pch=24, col="black", bg="red", cex=1.2)

par(xpd=T)

legend("topright",inset = c(-0.23,0), legend=c("Control","RNase", "Global", "Local"), pch=c(NA, NA, 21, 24), lty=c(1,1,NA,NA), col=c("green","red","black","black"), lwd = c(2,2,1.5,1.5))

rm(gene.name)
```