---
title: "Topic 3: Proteome-wide Screen for RNA-dependent Proteins; Subtopic 3: HeLa synchronized in Interphase"
author: "Hannah, Johann, Kira, Viktor"
date: "2023-04-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Topic 3: Proteome-wide Screen for RNA-dependent Proteins

#### Subtopic 3: HeLa Cells Synchronized in Interphase

First, we will load the dataset containing the mass spectrometry data from HeLa cells synchronized in interphase:

```{r}
RDeeP_HeLa_Interphase = read.csv("https://www.dropbox.com/s/nm9bgsyg7cv6wu1/RDeeP_HeLa_Interphase.csv?dl=1", header=TRUE, row.names=1, sep = ";")
head(RDeeP_HeLa_Interphase)
```

Are there any missing values in the dataset?

```{r}
sum(is.na(RDeeP_HeLa_Interphase))
```

Are there any rows that only contain zeros?

```{r}
which(rowSums(RDeeP_HeLa_Interphase)==0)
```

We can also split the dataset into two seperate datasets that contain the Control and RNase values:
#### 1.1 Split Dataset into Control and RNase

```{r}
RDeeP_HeLa_Interphase_Ctrl = cbind(RDeeP_HeLa_Interphase[,1:3],RDeeP_HeLa_Interphase[,7:9],RDeeP_HeLa_Interphase[,13:15],RDeeP_HeLa_Interphase[,19:21],RDeeP_HeLa_Interphase[,25:27],RDeeP_HeLa_Interphase[,31:33],RDeeP_HeLa_Interphase[,37:39],RDeeP_HeLa_Interphase[,43:45],RDeeP_HeLa_Interphase[,49:51],RDeeP_HeLa_Interphase[,55:57],RDeeP_HeLa_Interphase[,61:63],RDeeP_HeLa_Interphase[,67:69],RDeeP_HeLa_Interphase[,73:75],RDeeP_HeLa_Interphase[,79:81],RDeeP_HeLa_Interphase[,85:87],RDeeP_HeLa_Interphase[,91:93],RDeeP_HeLa_Interphase[,97:99],RDeeP_HeLa_Interphase[,103:105],RDeeP_HeLa_Interphase[,109:111],RDeeP_HeLa_Interphase[,115:117],RDeeP_HeLa_Interphase[,121:123],RDeeP_HeLa_Interphase[,127:129],RDeeP_HeLa_Interphase[,133:135],RDeeP_HeLa_Interphase[,139:141],RDeeP_HeLa_Interphase[,145:147])
RDeeP_HeLa_Interphase_RNase=RDeeP_HeLa_Interphase[,-which(names(RDeeP_HeLa_Interphase) %in% colnames(RDeeP_HeLa_Interphase_Ctrl))]
```

#### 1.2 NA Values and Zero Rows
```{r}
## Überprüfen welche Reihen in den Datasets nur Nullen enthalten

which(rowSums(RDeeP_HeLa_Interphase_Ctrl)==0)
which(rowSums(RDeeP_HeLa_Interphase_RNase)==0)

## Löschen der Nullreihen im Controldataset

RDeeP_HeLa_Interphase_Ctrl <- RDeeP_HeLa_Interphase_Ctrl[!(rownames(RDeeP_HeLa_Interphase_Ctrl)%in% c("FHOD3_HUMAN","P210L_HUMAN","PKD1_HUMAN","TGM7_HUMAN","KIF1A_HUMAN")),]

##Löschen der Nullreihen im RNase-Dataset

RDeeP_HeLa_Interphase_RNase <- RDeeP_HeLa_Interphase_RNase[!(rownames(RDeeP_HeLa_Interphase_RNase) %in% c("FHOD3_HUMAN","P210L_HUMAN","PKD1_HUMAN","TGM7_HUMAN", "KIF1A_HUMAN")),]
```

#### 1.4 Mean of Replicates

```{r}

# split RNase dataset into seperate datasets per fraction
RNase_01 <- RDeeP_HeLa_Interphase_RNase[,1:3]
RNase_02 <- RDeeP_HeLa_Interphase_RNase[,4:6]
RNase_03 <- RDeeP_HeLa_Interphase_RNase[,7:9]
RNase_04 <- RDeeP_HeLa_Interphase_RNase[,10:12]
RNase_05 <- RDeeP_HeLa_Interphase_RNase[,13:15]
RNase_06 <- RDeeP_HeLa_Interphase_RNase[,16:18]
RNase_07 <- RDeeP_HeLa_Interphase_RNase[,19:21]
RNase_08 <- RDeeP_HeLa_Interphase_RNase[,22:24]
RNase_09 <- RDeeP_HeLa_Interphase_RNase[,25:27]
RNase_10 <- RDeeP_HeLa_Interphase_RNase[,28:30]
RNase_11 <- RDeeP_HeLa_Interphase_RNase[,31:33]
RNase_12 <- RDeeP_HeLa_Interphase_RNase[,34:36]
RNase_13 <- RDeeP_HeLa_Interphase_RNase[,37:39]
RNase_14 <- RDeeP_HeLa_Interphase_RNase[,40:42]
RNase_15 <- RDeeP_HeLa_Interphase_RNase[,43:45]
RNase_16 <- RDeeP_HeLa_Interphase_RNase[,46:48]
RNase_17 <- RDeeP_HeLa_Interphase_RNase[,49:51]
RNase_18 <- RDeeP_HeLa_Interphase_RNase[,52:54]
RNase_19 <- RDeeP_HeLa_Interphase_RNase[,55:57]
RNase_20 <- RDeeP_HeLa_Interphase_RNase[,58:60]
RNase_21 <- RDeeP_HeLa_Interphase_RNase[,61:63]
RNase_22 <- RDeeP_HeLa_Interphase_RNase[,44:66]
RNase_23 <- RDeeP_HeLa_Interphase_RNase[,67:69]
RNase_24 <- RDeeP_HeLa_Interphase_RNase[,70:72]
RNase_25 <- RDeeP_HeLa_Interphase_RNase[,73:75]

# calculate mean of triplicates for each fraction
M_RNase_01 = as.data.frame(apply(RNase_01, 1, function(x) {mean(x)}))
M_RNase_02 = as.data.frame(apply(RNase_02, 1, function(x) {mean(x)}))
M_RNase_03 = as.data.frame(apply(RNase_03, 1, function(x) {mean(x)}))
M_RNase_04 = as.data.frame(apply(RNase_04, 1, function(x) {mean(x)}))
M_RNase_05 = as.data.frame(apply(RNase_05, 1, function(x) {mean(x)}))
M_RNase_06 = as.data.frame(apply(RNase_06, 1, function(x) {mean(x)}))
M_RNase_07 = as.data.frame(apply(RNase_07, 1, function(x) {mean(x)}))
M_RNase_08 = as.data.frame(apply(RNase_08, 1, function(x) {mean(x)}))
M_RNase_09 = as.data.frame(apply(RNase_09, 1, function(x) {mean(x)}))
M_RNase_10 = as.data.frame(apply(RNase_10, 1, function(x) {mean(x)}))
M_RNase_11 = as.data.frame(apply(RNase_11, 1, function(x) {mean(x)}))
M_RNase_12 = as.data.frame(apply(RNase_12, 1, function(x) {mean(x)}))
M_RNase_13 = as.data.frame(apply(RNase_13, 1, function(x) {mean(x)}))
M_RNase_14 = as.data.frame(apply(RNase_14, 1, function(x) {mean(x)}))
M_RNase_15 = as.data.frame(apply(RNase_15, 1, function(x) {mean(x)}))
M_RNase_16 = as.data.frame(apply(RNase_16, 1, function(x) {mean(x)}))
M_RNase_17 = as.data.frame(apply(RNase_17, 1, function(x) {mean(x)}))
M_RNase_18 = as.data.frame(apply(RNase_18, 1, function(x) {mean(x)}))
M_RNase_19 = as.data.frame(apply(RNase_19, 1, function(x) {mean(x)}))
M_RNase_20 = as.data.frame(apply(RNase_20, 1, function(x) {mean(x)}))
M_RNase_21 = as.data.frame(apply(RNase_21, 1, function(x) {mean(x)}))
M_RNase_22 = as.data.frame(apply(RNase_22, 1, function(x) {mean(x)}))
M_RNase_23 = as.data.frame(apply(RNase_23, 1, function(x) {mean(x)}))
M_RNase_24 = as.data.frame(apply(RNase_24, 1, function(x) {mean(x)}))
M_RNase_25  = as.data.frame(apply(RNase_25, 1, function(x) {mean(x)}))

#create new dataset combining the means for all 25 fractions
Mean_RNase = cbind(M_RNase_01, M_RNase_02, M_RNase_03, M_RNase_04, M_RNase_05, M_RNase_06, M_RNase_07, M_RNase_08, M_RNase_09, M_RNase_10, M_RNase_11, M_RNase_12, M_RNase_13, M_RNase_14, M_RNase_15, M_RNase_16, M_RNase_17, M_RNase_18, M_RNase_19, M_RNase_20, M_RNase_21, M_RNase_22, M_RNase_23, M_RNase_24, M_RNase_25)

colnames(Mean_RNase) <- c('Fraction1_RNase_Mean','Fraction2_RNase_Mean','Fraction3_RNase_Mean','Fraction4_RNase_Mean','Fraction5_RNase_Mean','Fraction6_RNase_Mean','Fraction7_RNase_Mean','Fraction8_RNase_Mean','Fraction9_RNase_Mean','Fraction10_RNase_Mean','Fraction11_RNase_Mean','Fraction12_RNase_Mean','Fraction13_RNase_Mean','Fraction14_RNase_Mean','Fraction15_RNase_Mean','Fraction16_RNase_Mean','Fraction17_RNase_Mean','Fraction18_RNase_Mean','Fraction19_RNase_Mean','Fraction20_RNase_Mean','Fraction21_RNase_Mean','Fraction22_RNase_Mean','Fraction23_RNase_Mean','Fraction24_RNase_Mean','Fraction25_RNase_Mean')

#####repeat for Control dataset
# split Ctrl dataset into seperate datasets per fraction
Ctrl_01 <- RDeeP_HeLa_Interphase_Ctrl[,1:3]
Ctrl_02 <- RDeeP_HeLa_Interphase_Ctrl[,4:6]
Ctrl_03 <- RDeeP_HeLa_Interphase_Ctrl[,7:9]
Ctrl_04 <- RDeeP_HeLa_Interphase_Ctrl[,10:12]
Ctrl_05 <- RDeeP_HeLa_Interphase_Ctrl[,13:15]
Ctrl_06 <- RDeeP_HeLa_Interphase_Ctrl[,16:18]
Ctrl_07 <- RDeeP_HeLa_Interphase_Ctrl[,19:21]
Ctrl_08 <- RDeeP_HeLa_Interphase_Ctrl[,22:24]
Ctrl_09 <- RDeeP_HeLa_Interphase_Ctrl[,25:27]
Ctrl_10 <- RDeeP_HeLa_Interphase_Ctrl[,28:30]
Ctrl_11 <- RDeeP_HeLa_Interphase_Ctrl[,31:33]
Ctrl_12 <- RDeeP_HeLa_Interphase_Ctrl[,34:36]
Ctrl_13 <- RDeeP_HeLa_Interphase_Ctrl[,37:39]
Ctrl_14 <- RDeeP_HeLa_Interphase_Ctrl[,40:42]
Ctrl_15 <- RDeeP_HeLa_Interphase_Ctrl[,43:45]
Ctrl_16 <- RDeeP_HeLa_Interphase_Ctrl[,46:48]
Ctrl_17 <- RDeeP_HeLa_Interphase_Ctrl[,49:51]
Ctrl_18 <- RDeeP_HeLa_Interphase_Ctrl[,52:54]
Ctrl_19 <- RDeeP_HeLa_Interphase_Ctrl[,55:57]
Ctrl_20 <- RDeeP_HeLa_Interphase_Ctrl[,58:60]
Ctrl_21 <- RDeeP_HeLa_Interphase_Ctrl[,61:63]
Ctrl_22 <- RDeeP_HeLa_Interphase_Ctrl[,44:66]
Ctrl_23 <- RDeeP_HeLa_Interphase_Ctrl[,67:69]
Ctrl_24 <- RDeeP_HeLa_Interphase_Ctrl[,70:72]
Ctrl_25 <- RDeeP_HeLa_Interphase_Ctrl[,73:75]

# calculate mean of triplicates for each fraction
M_Ctrl_01 = as.data.frame(apply(Ctrl_01, 1, function(x) {mean(x)}))
M_Ctrl_02 = as.data.frame(apply(Ctrl_02, 1, function(x) {mean(x)}))
M_Ctrl_03 = as.data.frame(apply(Ctrl_03, 1, function(x) {mean(x)}))
M_Ctrl_04 = as.data.frame(apply(Ctrl_04, 1, function(x) {mean(x)}))
M_Ctrl_05 = as.data.frame(apply(Ctrl_05, 1, function(x) {mean(x)}))
M_Ctrl_06 = as.data.frame(apply(Ctrl_06, 1, function(x) {mean(x)}))
M_Ctrl_07 = as.data.frame(apply(Ctrl_07, 1, function(x) {mean(x)}))
M_Ctrl_08 = as.data.frame(apply(Ctrl_08, 1, function(x) {mean(x)}))
M_Ctrl_09 = as.data.frame(apply(Ctrl_09, 1, function(x) {mean(x)}))
M_Ctrl_10 = as.data.frame(apply(Ctrl_10, 1, function(x) {mean(x)}))
M_Ctrl_11 = as.data.frame(apply(Ctrl_11, 1, function(x) {mean(x)}))
M_Ctrl_12 = as.data.frame(apply(Ctrl_12, 1, function(x) {mean(x)}))
M_Ctrl_13 = as.data.frame(apply(Ctrl_13, 1, function(x) {mean(x)}))
M_Ctrl_14 = as.data.frame(apply(Ctrl_14, 1, function(x) {mean(x)}))
M_Ctrl_15 = as.data.frame(apply(Ctrl_15, 1, function(x) {mean(x)}))
M_Ctrl_16 = as.data.frame(apply(Ctrl_16, 1, function(x) {mean(x)}))
M_Ctrl_17 = as.data.frame(apply(Ctrl_17, 1, function(x) {mean(x)}))
M_Ctrl_18 = as.data.frame(apply(Ctrl_18, 1, function(x) {mean(x)}))
M_Ctrl_19 = as.data.frame(apply(Ctrl_19, 1, function(x) {mean(x)}))
M_Ctrl_20 = as.data.frame(apply(Ctrl_20, 1, function(x) {mean(x)}))
M_Ctrl_21 = as.data.frame(apply(Ctrl_21, 1, function(x) {mean(x)}))
M_Ctrl_22 = as.data.frame(apply(Ctrl_22, 1, function(x) {mean(x)}))
M_Ctrl_23 = as.data.frame(apply(Ctrl_23, 1, function(x) {mean(x)}))
M_Ctrl_24 = as.data.frame(apply(Ctrl_24, 1, function(x) {mean(x)}))
M_Ctrl_25  = as.data.frame(apply(Ctrl_25, 1, function(x) {mean(x)}))

#create new dataset combining the means for all 25 fractions
Mean_Ctrl = cbind(M_Ctrl_01, M_Ctrl_02, M_Ctrl_03, M_Ctrl_04, M_Ctrl_05, M_Ctrl_06, M_Ctrl_07, M_Ctrl_08, M_Ctrl_09, M_Ctrl_10, M_Ctrl_11, M_Ctrl_12, M_Ctrl_13, M_Ctrl_14, M_Ctrl_15, M_Ctrl_16, M_Ctrl_17, M_Ctrl_18, M_Ctrl_19, M_Ctrl_20, M_Ctrl_21, M_Ctrl_22, M_Ctrl_23, M_Ctrl_24, M_Ctrl_25)

colnames(Mean_Ctrl) <- c('Fraction1_Ctrl_Mean','Fraction2_Ctrl_Mean','Fraction3_Ctrl_Mean','Fraction4_Ctrl_Mean','Fraction5_Ctrl_Mean','Fraction6_Ctrl_Mean','Fraction7_Ctrl_Mean','Fraction8_Ctrl_Mean','Fraction9_Ctrl_Mean','Fraction10_Ctrl_Mean','Fraction11_Ctrl_Mean','Fraction12_Ctrl_Mean','Fraction13_Ctrl_Mean','Fraction14_Ctrl_Mean','Fraction15_Ctrl_Mean','Fraction16_Ctrl_Mean','Fraction17_Ctrl_Mean','Fraction18_Ctrl_Mean','Fraction19_Ctrl_Mean','Fraction20_Ctrl_Mean','Fraction21_Ctrl_Mean','Fraction22_Ctrl_Mean','Fraction23_Ctrl_Mean','Fraction24_Ctrl_Mean','Fraction25_Ctrl_Mean')

#clearing the Environment of unnecessary data
remove(Ctrl_01, Ctrl_02, Ctrl_03, Ctrl_04, Ctrl_05, Ctrl_06, Ctrl_07, Ctrl_08, Ctrl_09, Ctrl_10, Ctrl_11, Ctrl_12, Ctrl_13, Ctrl_14, Ctrl_15, Ctrl_16, Ctrl_17, Ctrl_18, Ctrl_19, Ctrl_20, Ctrl_21, Ctrl_22, Ctrl_23, Ctrl_24, Ctrl_25,
RNase_01, RNase_02, RNase_03, RNase_04, RNase_05, RNase_06, RNase_07, RNase_08, RNase_09, RNase_10, RNase_11, RNase_12, RNase_13, RNase_14, RNase_15, RNase_16, RNase_17, RNase_18, RNase_19, RNase_20, RNase_21, RNase_22, RNase_23, RNase_24, RNase_25,
M_Ctrl_01, M_Ctrl_02, M_Ctrl_03, M_Ctrl_04, M_Ctrl_05, M_Ctrl_06, M_Ctrl_07, M_Ctrl_08, M_Ctrl_09, M_Ctrl_10, M_Ctrl_11, M_Ctrl_12, M_Ctrl_13, M_Ctrl_14, M_Ctrl_15, M_Ctrl_16, M_Ctrl_17, M_Ctrl_18, M_Ctrl_19, M_Ctrl_20, M_Ctrl_21, M_Ctrl_22, M_Ctrl_23, M_Ctrl_24, M_Ctrl_25,
M_RNase_01, M_RNase_02, M_RNase_03, M_RNase_04, M_RNase_05, M_RNase_06, M_RNase_07, M_RNase_08, M_RNase_09, M_RNase_10, M_RNase_11, M_RNase_12, M_RNase_13, M_RNase_14, M_RNase_15, M_RNase_16, M_RNase_17, M_RNase_18, M_RNase_19, M_RNase_20, M_RNase_21, M_RNase_22, M_RNase_23, M_RNase_24, M_RNase_25)

```

#### 1.5 Normalize Rows to 100

This will be done for the Control and RNase Datasets separately:

```{r}
Ctrl_Norm_100 = as.data.frame(sapply(RDeeP_HeLa_Interphase_Ctrl, function(i){(i/apply(RDeeP_HeLa_Interphase_Ctrl,1,sum))*100}))

RNase_Norm_100 = as.data.frame(sapply(RDeeP_HeLa_Interphase_RNase, function(i){(i/apply(RDeeP_HeLa_Interphase_RNase,1,sum))*100}))
```

#### 1.7 Data Exploration, First Graphical Representations

##### Without Normalization
```{r}
plot(1:25, Mean_Ctrl[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CTCF_HUMAN")
lines(1:25, Mean_RNase[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```
```{r}
plot(1:25, Mean_Ctrl[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CY24A_HUMAN")
lines(1:25, Mean_RNase[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```

##### With Normailzation 
```{r}
Mean_Ctrl_Norm_100 = as.data.frame(sapply(Mean_Ctrl, function(i){(i/apply(Mean_Ctrl,1,sum))*100}))

Mean_RNase_Norm_100 = as.data.frame(sapply(Mean_RNase, function(i){(i/apply(Mean_RNase,1,sum))*100}))
```

```{r}
plot(1:25, Mean_Ctrl_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CTCF_HUMAN Normalized", ylim=c(0,25))
lines(1:25, Mean_RNase_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CTCF_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```

```{r}
plot(1:25, Mean_Ctrl_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),],type="l",lwd=3,col="green",xlab="Fractions",ylab="Relative Protein Amount",main="CY24A_HUMAN Normailzed", ylim=c(0,18))
lines(1:25, Mean_RNase_Norm_100[which(rownames(RDeeP_HeLa_Interphase)==c("CY24A_HUMAN")),], type="l",lwd=3,col="red")
grid()
legend("topright",legend=c("Control","RNase"),col=c("green","red"),bg="white",lwd=2)
```

